Stat 534 Project: \\ Extrapolation from Poisson Process Intensity Surface Models

### 2017-04-03 project/paper.rnw
Fixed cache.

# Create a ppp object the uses the full region as the window.
ex_ppp_full <- ppp(ex_anom$x, ex_anom$y, window = site_window)

@@

<<packages, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<hw4_sim, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<hw4_fit_full, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<hw4_fit_s, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<hw4_plot, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<hw4_fitplot, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<uxoexampledata, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<truth, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<sim2000obs, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<quad1, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<polyfit2, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit3, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit4, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit5, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit6, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit7, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit8, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit9, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit10, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit11, echo = TRUE, eval = FALSE>>=
@
\vspace{-30pt}
<<polyfit12, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<polypred1, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<polyplot1, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<polyse1, echo = TRUE, eval = FALSE>>=
@
\vspace{-20pt}
<<dummy, echo = TRUE, eval = FALSE>>=
@

>>>>

# Create a ppp object that uses the full region as the window.
ex_ppp_full <- ppp(ex_anom$x, ex_anom$y, window = site_window)

@@

<<packages, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<hw4_sim, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<hw4_fit_full, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<hw4_fit_s, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<hw4_plot, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<hw4_fitplot, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<uxoexampledata, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<truth, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<sim2000obs, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<quad1, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<polyfit2, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit3, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit4, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit5, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit6, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit7, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit8, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit9, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit10, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit11, echo = TRUE, eval = FALSE>>=
@
\vspace{-25pt}
<<polyfit12, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<polypred1, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<polyplot1, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<polyse1, echo = TRUE, eval = FALSE>>=
@
\vspace{-15pt}
<<dummy, echo = TRUE, eval = FALSE>>=
@

### 2017-04-03 project/pres.rnw
Typos are a pain.
Fixed cache.

\item Log-likelihood of Poisson with intensity \(\lambda(\mathbf{s})\) on
region \(D\) (note typos in \textcite{digglebook})
\begin{align*}
\ell(\lambda) &= \left\{-\mu + n\log(\mu) - \log(n!)\right\}
+ \sum_{i=1}^{n}\left\{\log\left(\lambda(\mathbf{s}_{i})\right)
- \log(\mu)\right\} \\
&= \sum_{i=1}^{n}\log\left(\lambda(\mathbf{s}_{i})\right)
-\int_{D}\lambda(\mathbf{s})d\mathbf{s} - \log(n!).
\end{align*}
where \(\mu=\int_{D}\lambda(\mathbf{s})d\mathbf{s}\)
\end{itemize}

@@

<<polyfit, warning = FALSE, cache = TRUE, dependson = 'uxoexampledata'>>=
ex_fit1 <- ppm(ex_ppp ~ x + y)
ex_Q <- quad(data = ex_ppp, dummy = runifpoint(500000, Window(ex_ppp)))

ex_fit2 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 2), correction = 'iso')
ex_fit3 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 3), correction = 'iso')
ex_fit4 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 4), correction = 'iso')
ex_fit5 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 5), correction = 'iso')
ex_fit6 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 6), correction = 'iso')
ex_fit7 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 7), correction = 'iso')
ex_fit8 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 8), correction = 'iso')
ex_fit9 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 9), correction = 'iso')
ex_fit10 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 10), correction = 'iso')
ex_fit11 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 11), correction = 'iso')
ex_fit12 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 12), correction = 'iso')

ex_p2 <- predict(ex_fit2, window = site_window, se = TRUE)
ex_p3 <- predict(ex_fit3, window = site_window, se = TRUE)
ex_p4 <- predict(ex_fit4, window = site_window, se = TRUE)
ex_p5 <- predict(ex_fit5, window = site_window, se = TRUE)
ex_p6 <- predict(ex_fit6, window = site_window, se = TRUE)
ex_p7 <- predict(ex_fit7, window = site_window, se = TRUE)
ex_p8 <- predict(ex_fit8, window = site_window, se = TRUE)
ex_p9 <- predict(ex_fit9, window = site_window, se = TRUE)
ex_p10 <- predict(ex_fit10, window = site_window, se = TRUE)
ex_p11 <- predict(ex_fit11, window = site_window, se = TRUE)
ex_p12 <- predict(ex_fit12, window = site_window, se = TRUE)
@

<<resplots1, cache = TRUE, dependson = 'polyfit'>>=
par(mfrow = c(2, 3), mar = c(1, 0, 1.2, 3), las = 2, cex = 1)
plot(43560 * ex_p2$estimate, main = '2nd Degree Polynom')
plot(43560 * ex_p3$estimate, main = '3rd Degree Polynom')
plot(43560 * ex_p4$estimate, main = '4th Degree Polynom')
plot(43560 * ex_p5$estimate, main = '5th Degree Polynom')
plot(43560 * ex_p6$estimate, main = '6th Degree Polynom')
plot(43560 * ex_p7$estimate, main = '7th Degree Polynom')
@

@@

<<resplots2, cache = TRUE, dependson = 'polyfit'>>=
par(mfrow = c(2, 3), mar = c(1, 0, 1.2, 3), las = 2, cex = 1)
plot(43560 * ex_p8$estimate, main = '8th Degree Polynom')
plot(43560 * ex_p9$estimate, main = '9th Degree Polynom')
plot(43560 * ex_p10$estimate, main = '10th Degree Polynom')
plot(43560 * ex_p11$estimate, main = '11th Degree Polynom')
plot(43560 * ex_p12$estimate, main = '12th Degree Polynom')
plot(43560 * density(ex_ppp_full) * area(ex_ppp_full) / area(ex_ppp),
     main = 'Kernel Density')
@

>>>>

\item Log-likelihood of Poisson with intensity \(\lambda(\mathbf{s})\) on
region \(D\) (note typos in \textcite{digglebook})
\begin{align*}
\ell(\lambda) &= \left\{-\mu + n\log(\mu) - \log(n!)\right\}
+ \sum_{i=1}^{n}\left\{\log\left(\lambda(\mathbf{s}_{i})\right)
- \log(\mu)\right\} \\
&= \sum_{i=1}^{n}\log\left(\lambda(\mathbf{s}_{i})\right)
-\int_{D}\lambda(\mathbf{s})d\mathbf{s} - \log(n!)
\end{align*}
where \(\mu=\int_{D}\lambda(\mathbf{s})d\mathbf{s}\)
\end{itemize}

@@

<<polyfit, warning = FALSE, cache = TRUE, dependson = 'uxoexampledata'>>=
ex_fit1 <- ppm(ex_ppp ~ x + y)
ex_Q <- quad(data = ex_ppp, dummy = runifpoint(500000, Window(ex_ppp)))
@
<<polyfit2, cache = TRUE, dependson = 'polyfit'>>=
ex_fit2 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 2), correction = 'iso')
@
<<polyfit3, cache = TRUE, dependson = 'polyfit'>>=
ex_fit3 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 3), correction = 'iso')
@
<<polyfit4, cache = TRUE, dependson = 'polyfit'>>=
ex_fit4 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 4), correction = 'iso')
@
<<polyfit5, cache = TRUE, dependson = 'polyfit'>>=
ex_fit5 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 5), correction = 'iso')
@
<<polyfit6, cache = TRUE, dependson = 'polyfit'>>=
ex_fit6 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 6), correction = 'iso')
@
<<polyfit7, cache = TRUE, dependson = 'polyfit'>>=
ex_fit7 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 7), correction = 'iso')
@
<<polyfit8, cache = TRUE, dependson = 'polyfit'>>=
ex_fit8 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 8), correction = 'iso')
@
<<polyfit9, cache = TRUE, dependson = 'polyfit'>>=
ex_fit9 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 9), correction = 'iso')
@
<<polyfit10, cache = TRUE, dependson = 'polyfit'>>=
ex_fit10 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 10), correction = 'iso')
@
<<polyfit11, cache = TRUE, dependson = 'polyfit'>>=
ex_fit11 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 11), correction = 'iso')
@
<<polyfit12, cache = TRUE, dependson = 'polyfit'>>=
ex_fit12 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 12), correction = 'iso')
@

<<polypred>>=
ex_p2 <- predict(ex_fit2, window = site_window, se = TRUE)
ex_p3 <- predict(ex_fit3, window = site_window, se = TRUE)
ex_p4 <- predict(ex_fit4, window = site_window, se = TRUE)
ex_p5 <- predict(ex_fit5, window = site_window, se = TRUE)
ex_p6 <- predict(ex_fit6, window = site_window, se = TRUE)
ex_p7 <- predict(ex_fit7, window = site_window, se = TRUE)
ex_p8 <- predict(ex_fit8, window = site_window, se = TRUE)
ex_p9 <- predict(ex_fit9, window = site_window, se = TRUE)
ex_p10 <- predict(ex_fit10, window = site_window, se = TRUE)
ex_p11 <- predict(ex_fit11, window = site_window, se = TRUE)
ex_p12 <- predict(ex_fit12, window = site_window, se = TRUE)
@

<<resplots1>>=
par(mfrow = c(2, 3), mar = c(1, 0, 1.2, 3), las = 2, cex = 1)
plot(43560 * ex_p2$estimate, main = '2nd Degree Polynom')
plot(43560 * ex_p3$estimate, main = '3rd Degree Polynom')
plot(43560 * ex_p4$estimate, main = '4th Degree Polynom')
plot(43560 * ex_p5$estimate, main = '5th Degree Polynom')
plot(43560 * ex_p6$estimate, main = '6th Degree Polynom')
plot(43560 * ex_p7$estimate, main = '7th Degree Polynom')
@

@@

<<resplots2>>=
par(mfrow = c(2, 3), mar = c(1, 0, 1.2, 3), las = 2, cex = 1)
plot(43560 * ex_p8$estimate, main = '8th Degree Polynom')
plot(43560 * ex_p9$estimate, main = '9th Degree Polynom')
plot(43560 * ex_p10$estimate, main = '10th Degree Polynom')
plot(43560 * ex_p11$estimate, main = '11th Degree Polynom')
plot(43560 * ex_p12$estimate, main = '12th Degree Polynom')
plot(43560 * density(ex_ppp_full) * area(ex_ppp_full) / area(ex_ppp),
     main = 'Kernel Density')
@
